### 2014-12-18 figures/LG-Operation-Scenario-02-Mobile-Mining.tex
Added Privacy Protection tex from Max.
Signed-off-by: Heinrich Hartmann <hartmann@uni-koblenz.de>

\begin{figure}[h]
\centering
\includegraphics{diagrams/png/scenario01-ServerSideMining.png}

\begin{flushleft}
\scriptsize
\textbf{Legend:}
\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \textbf{(a) Citizen:} User of the L+G client application whose privacy
  is at stake.
\item
  \textbf{(b) Mobile Device:} Runs the L+G client application, produces
  and stores data sensitive to the users privacy.
\item
  \textbf{(c) L+G Data Center:} Runs the L+G services, proccesses and
  stores user data.
\item
  \textbf{(d) L+G Maintenance Crew:} Technical staff with access to
  critical infrastructure.
\item
  \textbf{(e) Aggregation Monitor:} Interface to aggregated user data.
\item
  \textbf{(f) Local Authority:} Provider of the L+G system.
\end{itemize}
\end{flushleft}

\caption{Live+Gov Operation Scenario 01 - Server Side Mining}
\label{figure:Live+Gov Operation Scenario 01 - Server Side Mining}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=\textwidth]{diagrams/png/scenario02-MobileMining.png}

\begin{flushleft}
\scriptsize
\textbf{Legend:}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \textbf{(a) Citizen:} User of the L+G client application whose privacy
  is at stake.
\item
  \textbf{(b) Mobile Device:} Runs the L+G client application, produces
  and stores data sensitive to the users privacy.
\item
  \textbf{(c) L+G Data Center:} Runs the L+G services, proccesses and
  stores user data.
\item
  \textbf{(d) L+G Maintenance Crew:} Technical staff with access to
  critical infrastructure.
\item
  \textbf{(e) Aggregation Monitor:} Interface to aggregated user data.
\item
  \textbf{(f) Local Authority:} Provider of the L+G system.
\end{itemize}
\end{flushleft}

\caption{Live+Gov Operation Scenario 02 - Mobile Mining}
\label{figure:Live+Gov Operation Scenario 02 - Mobile Mining}
\end{figure}
